Untitled

### 2017-02-14 Code/calculate_std_mort_rates.Rmd
update std mort plots

>>>>

```{r calculate_difference_in_mortality}
mortality.rates.white <- mortality.rates %>% filter(race == "White") %>% 
  select(sex, state, year, COD, post.samp, age.std.mortality.rate, rate.per.100k) %>%
  rename(age.std.mortality.rate.white = age.std.mortality.rate,
         rate.per.100k.white = rate.per.100k)

mortality.rates.black <- mortality.rates %>% filter(race == "Black") %>% 
  rename(age.std.mortality.rate.black = age.std.mortality.rate,
         rate.per.100k.black = rate.per.100k)

mortality.rates.wide <- merge(mortality.rates.black, mortality.rates.white, by = c("post.samp", "sex", "state", "year", "COD"))

mortality.rates.wide <- mortality.rates.wide %>% mutate(rate.difference = rate.per.100k.black - rate.per.100k.white)

write.csv(mortality.rates.wide, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Data/mortality_rates_wide.csv")
```
